Impact of Bank of Canada's Monetary Policy on Consumer Debt Levels

### 2024-04-20 paper/paper.qmd
Resolved merge conflicts

The model's primary explanatory variable is the short-term interest rate, represented by the IRSTCB01CAM156N variable, sourced from the dataset on short-term interest rates. This variable serves as a proxy for changes in the Bank of Canada's monetary policy stance, capturing variations in borrowing costs and the availability of credit in the economy.

>>>>

The model's primary explanatory variable is the short-term interest rate, represented by the interest_rates variable, sourced from the dataset on short-term interest rates. This variable serves as a proxy for changes in the Bank of Canada's monetary policy stance, capturing variations in borrowing costs and the availability of credit in the economy.
